QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`

### 2024-02-29 minos/outcomes/QALY_comparison2.Rmd
Slight tweak to the QALY calculation and tidied up the QALY outcomes makefile. Also improvements to the generic visualisation script

---
params:
  experiment: ''
  base: ''
  intervention: ''
title: "QALY Comparisons - r`experiment` - r`intervention` - r`baseline`"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

```{r}
# experiment <- params$experiment
# base <- params$base
# intervention <- params$intervention

experiment <- 'default_config'
baseline <- 'baseline'
intervention <- '100All'
```

>>>>

---
params:
  experiment: 'default_config/'
  base: 'baseline'
  intervention: '50All'
title: "QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

```{r}
experiment <- params$experiment
baseline <- params$base
intervention <- params$intervention
# 
# experiment <- 'default_config'
# baseline <- 'baseline'
# intervention <- '100All'
```
